---
title: "Smoke Outlook for `r params$BURN_NAME` Prescribed Fire, `r params$FOREST`"
# date: "Issued at `r Sys.time()`"
output: html_document
geometry: margin=0.25in
params: 
  BURN_NAME: "TEST"
  FOREST: "TEST"
  AUTHOR: "TEST"
  EMAIL: "TEST"
  PHONE: "TEST"
  RUN_ID: "164b1a4537ae73"
  DROP_LOW_AVG: "No"
  FORECAST_AQI_SELECT: "No"
  SUPERFOG_SCREEN_SELECT: "No"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
  library(tidyverse)            # tidyverse
  library(ggimage)              # add images to ggplot figures
  library(gridExtra)            # multi-plot arrangement
  library(ggrepel)              # label arrangement for ggplot
  library(ggmap)                # basemap for AQI monitors
  library(png)                  # reading in PNGs from BSky
  library(curl)                 # downloading data from BSky dispersion results
  library(RCurl)                 # downloading data from BSky dispersion results
  library(rjson)                # reading JSON data
  library(lubridate)            # date manipulation
  library(terra)                # raster manipulation       
  library(sf)                   # spatial data
  library(kableExtra)           # styling of kable objects
  library(leaflet)              # interactive mapping
  library(egg)
  
  
  # Mazama Science packages
  library(beakr)                # web service framework
  library(MazamaCoreUtils)      # cache management and more
  library(AirMonitor)           # air quality data

```


```{r burn_info, include = FALSE}
##***************************************
## FIND MOST RECENT MODEL RUN AND CORRECT SERVER LINK 
##***************************************

# general dispersion results link
bsky_link <- paste("https://tools.airfire.org/playground/v3.5/dispersionresults.php?scenario_id=",
                   params$RUN_ID,
                   sep = "")

# links for results output from both servers
serv1_link <- paste("https://playground-1.airfire.org/bluesky-web-output/",
                      params$RUN_ID,
                      "-dispersion",
                      sep = "")

serv2_link <- paste("https://playground-2.airfire.org/bluesky-web-output/",
                    params$RUN_ID,
                    "-dispersion",
                    sep = "")

serv_links_ls <- list(serv1_link, serv2_link)
names(serv_links_ls) <- c("serv1_link", 
                          "serv2_link")


# get info on end time of simulation for each server
date_info_1 <- if (url.exists(serv1_link)) {
  
  # pull end time from output.json
  end_time_val <- lubridate::as_datetime(fromJSON(file = paste(serv1_link, "/output.json", sep = ""))$runtime[["end"]])
  
  # create df
  end_time_df <- tibble(server = "serv1_link",
                        end_time = end_time_val)
  
}else{
  # create df
  end_time_df <- tibble(server = NA,
                        end_time = NA)}



date_info_2 <- if (url.exists(serv2_link)) {
  
  # pull end time from output.json
  end_time_val <- lubridate::as_datetime(fromJSON(file = paste(serv2_link, "/output.json", sep = ""))$runtime[["end"]])
  
  # create df
  end_time_df <- tibble(server = "serv2_link",
                        end_time = end_time_val)
  
}else{
  # create df
  end_time_df <- tibble(server = NA,
                        end_time = NA)}

# combine outputs, select most recent model and set results_link to correct url
recent_server <- bind_rows(date_info_1, date_info_2) %>% 
  arrange(desc(end_time)) %>% 
  slice(1) %>% 
  pull(server)

results_output_link <- serv_links_ls[[recent_server]]


## CREATE DATAFRAME OF BASIC FIRE INFO  ----------------------------------------------

# basic burn information
burn_info <- read.csv(paste(results_output_link, "/output/data/fire_locations.csv", sep = "")) %>% 
  dplyr::select(lat = latitude,
         lon = longitude,
         utc_offset,
         date_time,
         acres = area) %>% 
  mutate(date = as_date(ymd(date_time)))

# create sf object of burn location
burn_loc <- burn_info %>% 
  dplyr::select(lon, lat)

# create sf object of burn location
burn_loc_sf <- st_as_sf(burn_loc,
                        coords = c("lon", "lat"),
                        crs = st_crs("EPSG:4326"))

# read in dispersion breakpoints and id the state where burn is happening
regions <- st_read("region") #for testing: replace with "../gis/regions"
regions_sf <- st_transform(regions, crs = st_crs(burn_loc_sf))
burn_region <- as.character(regions$REGION[st_intersects(burn_loc_sf, regions_sf)[[1]]])

# update burn info with region
burn_info <- burn_info %>% 
  mutate(region = burn_region)


## GENERTE DATA FOR RECENT AIR QUALITY ----------------------------------------------

# pull hourly data within 300 km of rx burn 
airnow <- airnow_loadLatest() %>% 
  monitor_filterByDistance(longitude = burn_info$lon, 
                           latitude = burn_info$lat, 
                           radius = 300000, # 300km
                           addToMeta = TRUE) 

# subset to nearest 5 monitors
near_5 <- airnow$meta %>% 
  arrange(distanceFromTarget) %>% 
  slice(1:5)

# filter to 3 days before burn and get mean values
near_5_df <- airnow$data %>% 
  dplyr::select(datetime, any_of(near_5$deviceDeploymentID)) %>% 
  mutate(datetime = ymd(as_date(datetime))) %>% 
  filter(datetime >= (ymd(as_date(Sys.time())) - 3) & datetime <= (ymd(as_date(Sys.time())) - 1)) %>% 
  group_by(datetime) %>% 
  summarise_all(.funs = mean, na.rm = TRUE) %>% 
  ungroup() %>% 
  gather(deviceDeploymentID, pm_val, -datetime) %>% 
  mutate(aqi_col = aqiColors(pm_val,
                             pollutant = c("PM2.5"),
                             palette = c("EPA")),
         aqi_cat = cut(pm_val, 
                       breaks = US_AQI$breaks_AQI,
                       labels = US_AQI$names_eng)) %>% 
  left_join(., airnow$meta) %>% 
  mutate(siteName = str_to_title(locationName))

# most recent daily AQI
rec_daily_df <- near_5_df %>% 
  filter(datetime == max(datetime)) %>% 
  mutate(siteName = str_to_title(locationName))

# read aqi table to include in final output
aqi_tab <- read_csv("aqi_table.csv")


# create contact info object
contact_info <- tibble(name = if(params$AUTHOR != "") {params$AUTHOR} else{NA},
                       phone = if(params$PHONE != "") {params$PHONE} else{NA},
                       email = if(params$EMAIL != "") {params$EMAIL} else{NA}) %>% 
  select_if(~ !any(is.na(.))) %>% 
  unite("contact", sep=", ") %>% 
  dplyr::pull(contact)

# forecasted AQI statement
forecast_aqi_sen <- if(burn_info$region == "08") {paste("**The forecasted AQI for areas downwind of the planned burn is ",
                                                                      params$FORECAST_AQI_SELECT,
                                                                      ".**",
                                                                      sep = "")} else{""}

# superfog statement
# superfog_sen <- if(params$SUPERFOG_SCREEN_SELECT == "Yes") {"*The spot weather forecast indicates there is potential for superfog formation in the overnight hours. Please see separate modeling output from PB Piedmont to look at nighttime dispersion and areas with elevated chances of superfog formation.*"} else{"*The spot weather forecast indicates there is not potential for superfog formation in the overnight hours.*"}

# superfog_sen <- ifelse(is.null(params$SUPERFOG_SCREEN_SELECT), 
#                          NULL,
#                        ifelse(params$SUPERFOG_SCREEN_SELECT == "Yes",
#                               "*The spot weather forecast indicates there is potential for superfog formation in the overnight hours. Please see separate modeling output from PB Piedmont to look at nighttime dispersion and areas with elevated chances of superfog formation.*",
#                               "*The spot weather forecast indicates there is not potential for superfog formation in the overnight hours.*"))


superfog_sen <- ifelse(burn_info$region == "08",
                       ifelse(params$SUPERFOG_SCREEN_SELECT == "Yes",
                              "**The spot weather forecast indicates there is potential for superfog formation in the overnight hours. Please see separate modeling output from PB Piedmont to look at nighttime dispersion and areas with elevated chances of superfog formation.**",
                              "**The spot weather forecast indicates there is not potential for superfog formation in the overnight hours.**"),
                       "")



```



This report documents the recent air quality, smoke analysis and weather forecast for the `r params$BURN_NAME` prescribed fire on the `r params$FOREST`, planned for `r burn_info$date`. Additional smoke modeling output can be found at the [BlueSky Playground Dispersion Results](`r bsky_link`). For more information: `r contact_info`.


## Recent Air Quality in Area 

Shown below is the recently measured air quality index (AQI) in the area. The map shows the location of the burn and the most recent daily AQI for nearby permanent monitors. The figure shows the daily AQI for the previous 3 days for the monitors in the map. Additional information for your area, including AQI forecasts, can be found at the [EPA AirNow Map](https://gispub.epa.gov/airnow/). `r if(!(is.null(params$FORECAST_AQI_SELECT))){forecast_aqi_sen}`

```{r burn_map_aqi, out.width="100%", include = TRUE, echo = FALSE, message = FALSE, warning = FALSE}
## CREATE MAP OF BURN AND NEARBY AQ MONITORS ----------------------------------------------

# read in burn icon for mapping
burn_icon <- tibble(x = burn_info$lon,
                        y = burn_info$lat,
                        image = "redFlame.png")


# pull burn map from Open Street Maps
register_stadiamaps("f9cffd73-4030-4d4b-8294-bddb274018ca")
burn_map_info <- get_stadiamap(c(left = burn_info$lon - 1, bottom = burn_info$lat - 1, 
                                 right = burn_info$lon + 1, top = burn_info$lat + 1),
                         maptype = "outdoors",
                         zoom = 9)


# plot burn map
burn_map <- ggmap(burn_map_info, extent = "device") +
  geom_image(aes(x = x, y = y, image = image), data = burn_icon) +
  geom_point(aes(x = longitude, y = latitude, color = aqi_cat), size = 6, show.legend = FALSE, data = rec_daily_df) +
  geom_label_repel(aes(x = longitude, y = latitude, label=siteName),
                   box.padding = 1,
                   arrow = arrow(length = unit(0.02, "npc")),
                   data = rec_daily_df) +
  scale_color_manual(values = rec_daily_df$aqi_col) +
  theme_minimal()  +
  theme(axis.text = element_blank(),
        axis.title = element_blank())


# recent AQI values at nearby monitors
daily_aqi_plot <- ggplot(aes(x = datetime, y = pm_val, group = siteName), data = near_5_df) +
  geom_bar(aes(fill = aqi_cat), stat = "identity", show.legend = FALSE) +
  scale_fill_manual(values = US_AQI$colors_EPA) +
  facet_wrap(~siteName, ncol = 1) +
  labs(y = bquote(~PM[2.5]~(ug~m^{-3})), x = NULL) +
  theme_minimal() +
  theme(axis.title.y  = element_text(size = 9))


# aqi_table 
aqi_kable <- aqi_tab %>%
  mutate('Air Quality Index (AQI)' = cell_spec(c("Good", "Moderate", "USG", "Unhealthy", "Very Unhealthy", "Hazardous"), 
                                               color = c("black", "black", "black", "white", "white", "white"), bold = T, format = "html", background = US_AQI$colors_EPA)) %>% 
  kable(escape = FALSE, linesep = "", format = "html" ) %>%
  kable_styling(full_width = F, position = "center")
 
# show the burn map and aqi side-by-side
grid.arrange(burn_map, daily_aqi_plot, nrow = 1, widths = c(2:1))

# show aqi color scheme and explanations
aqi_kable


```

**Note**: Generally, smoke sensitive people are kids and older adults along with those who have cardiovascular or respiratory conditions.

For more smoke and health information: [https://airnow.gov/](https://airnow.gov/)


## Modeled Smoke Dispersion
Below are the smoke modeling outputs for the day of the planned burn. The maps below show the __daily average concentrations__ (top panel) and __daily average visual range__ (bottom panel) for `r burn_info$date`. Zoom in/out on each of the interactive maps to view particular features.


```{r leaflet_map_data_mgt, include = FALSE, echo = FALSE, message = FALSE, warning = FALSE}

## READ IN POP/SVI DATA ----------------------------------------------

# census data
pop <- readRDS("population_aggregate_factor.rds") 

# SVI data
svi <- readRDS("svi.rds") 


## DOWNLOAD DATA FROM BSKY DISPERSION RESULTS ----------------------------------------------

# create outlook directory
dir.create("temp")
outlook_path <- "temp"
  
# smoke dispersion
smoke_disp_link <- paste(results_output_link,
                         "/output/smoke_dispersion.kmz", sep = "")

# download smoke dispersion into a zip and regular version 
curl_download(smoke_disp_link, destfile = paste(outlook_path,
                                                "/smoke_dispersion.kmz.zip",
                                                sep = ""))
# unzip the file
unzip(zipfile = paste(outlook_path,
                      "/smoke_dispersion.kmz.zip",
                      sep = ""),
      exdir = outlook_path)

# get rid of zip file
file.remove(paste(outlook_path,
                  "/smoke_dispersion.kmz.zip",
                  sep = ""))

# grid info to get extent of png files
grid_info_link <- paste(results_output_link, 
                        "/output/grid_info.json", sep = "")

# download grid info
grid_info <- fromJSON(file=paste(results_output_link, 
                    "/output/grid_info.json", sep = ""))[[1]]


## READ IN SMOKE DISPERSION RESULTS AND RECODE FOR PLOTTING ----------------------------------------------

# read in hex codes
avg_pal <- read_csv("bsky_new_color_ramp.csv") 
vis_pal <- read_csv("bsky_vis_color_ramp.csv") 


# burn CRS
burn_crs <- st_crs(read_sf(paste(outlook_path,
                                 "/doc.kml", sep = "")))

# read PNG files
day_one_vis <- readPNG(paste(outlook_path,
                             "/visualrange_100m_daily_minimum_UTC",
                             gsub(":", "", burn_info$utc_offset),
                             "_RainbowColorBarVisualRange_",
                             burn_info$date_time, 
                             ".png", sep = ""))


day_one_avg <- readPNG(paste(outlook_path,
                             "/pm25_100m_daily_average_UTC",
                             gsub(":", "", burn_info$utc_offset),
                            "_GreyColorBar_",
                             burn_info$date_time, 
                             ".png", sep = ""))

# collapse RGB bands into one with hex codes as values
day_one_vis_r <- as.raster(day_one_vis)
day_one_avg_r <- as.raster(day_one_avg)



# replace hex codes with PM categories, including an option whether to code the lowest category as NA
day_one_avg_r[day_one_avg_r == "#CCE5FFB2"] <- ifelse(params$DROP_LOW_AVG == "Yes", 
                                                      avg_pal$pm[avg_pal$hex == "#00000000"],
                                                      avg_pal$pm[avg_pal$hex == "#CCE5FFB2"])
day_one_avg_r[day_one_avg_r == "#99CCFFB2"] <- avg_pal$pm[avg_pal$hex == "#99CCFFB2"] #2
day_one_avg_r[day_one_avg_r == "#0D98BAB2"] <- avg_pal$pm[avg_pal$hex == "#0D98BAB2"] #3
day_one_avg_r[day_one_avg_r == "#9ACD32B2"] <- avg_pal$pm[avg_pal$hex == "#9ACD32B2"] #4
day_one_avg_r[day_one_avg_r == "#FFFF00B2"] <- avg_pal$pm[avg_pal$hex == "#FFFF00B2"] #5
day_one_avg_r[day_one_avg_r == "#FF6600B2"] <- avg_pal$pm[avg_pal$hex == "#FF6600B2"] #6
day_one_avg_r[day_one_avg_r == "#C71585B2"] <- avg_pal$pm[avg_pal$hex == "#C71585B2"] #7
day_one_avg_r[day_one_avg_r == "#2B0A78B2"] <- avg_pal$pm[avg_pal$hex == "#2B0A78B2"] #8
day_one_avg_r[day_one_avg_r == "#00000000"] <- avg_pal$pm[avg_pal$hex == "#00000000"] #0


day_one_vis_r[day_one_vis_r == "#2B0A78B2"] <- vis_pal$miles[vis_pal$hex == "#2B0A78B2"]  #1
day_one_vis_r[day_one_vis_r == "#722789B2"] <- vis_pal$miles[vis_pal$hex == "#722789B2"] #2
day_one_vis_r[day_one_vis_r == "#C71585B2"] <- vis_pal$miles[vis_pal$hex == "#C71585B2"] #3
day_one_vis_r[day_one_vis_r == "#FF0000B2"] <- vis_pal$miles[vis_pal$hex == "#FF0000B2"] #4
day_one_vis_r[day_one_vis_r == "#FF0000B2"] <- vis_pal$miles[vis_pal$hex == "#FF0000B2"] #5
day_one_vis_r[day_one_vis_r == "#FFFF00B2"] <- vis_pal$miles[vis_pal$hex == "#FFFF00B2"] #6
day_one_vis_r[day_one_vis_r == "#9ACD32B2"] <- vis_pal$miles[vis_pal$hex == "#9ACD32B2"] #6
day_one_vis_r[day_one_vis_r == "#00FF00B2"] <- vis_pal$miles[vis_pal$hex == "#00FF00B2"] #6
day_one_vis_r[day_one_vis_r == "#0D98BAB2"] <- vis_pal$miles[vis_pal$hex == "#0D98BAB2"] #0
day_one_vis_r[day_one_vis_r == "#0000FFB2"] <- vis_pal$miles[vis_pal$hex == "#0000FFB2"] #5
day_one_vis_r[day_one_vis_r == "#99CCFFB2"] <- vis_pal$miles[vis_pal$hex == "#99CCFFB2"] #6
day_one_vis_r[day_one_vis_r == "#CCE5FFB2"] <- vis_pal$miles[vis_pal$hex == "#CCE5FFB2"] #6
day_one_vis_r[day_one_vis_r == "#FFFFFFB2"] <- vis_pal$miles[vis_pal$hex == "#FFFFFFB2"] #6
day_one_vis_r[day_one_vis_r == "#00000000"] <- vis_pal$miles[vis_pal$hex == "#00000000"] #0


# convert to matrix and change values to numeric
day_one_vis_m <- matrix(as.numeric(day_one_vis_r),
                        nrow = dim(day_one_vis_r)[1],
                        ncol = dim(day_one_vis_r)[2],
                        byrow = TRUE)

day_one_avg_m <- matrix(as.numeric(day_one_avg_r),
                        nrow = dim(day_one_avg_r)[1],
                        ncol = dim(day_one_avg_r)[2],
                        byrow = TRUE)


# convert to raster
day_one_vis_ras <- rast(day_one_vis_m)
day_one_avg_ras <- rast(day_one_avg_m)


# ratify raster (convert to factor)
day_one_vis_ras <- as.factor(day_one_vis_ras)
day_one_avg_ras <- as.factor(day_one_avg_ras)

# data frame of levels for day one vis including/excluding lowest level
vis_levels <- list(data.frame(ID = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12", "13"),
                                    vis = c("0.00-0.04", "0.04-0.08", "0.08-0.15", "0.15-0.25", "0.25-0.50", "0.50-1", "1-2", "2-3", "3-4", "4-5", "5-20", "20-50", ">50" )))


# data frame of levels for day one avg including/excluding lowest level
avg_levels_w_low <- list(data.frame(ID = c("1", "2", "3", "4", "5", "6", "7", "8"),
                                    pm = c("1-12", "12-35", "35-55", "55-150", "150-250", "250-350", "350-500", ">500")))

avg_levels_wo_low <- list(data.frame(ID = c("2", "3", "4", "5", "6", "7", "8"),
                                     pm = c("12-35", "35-55", "55-150", "150-250",  "250-350", "350-500", ">500")))



# add levels of factor in dataframe
levels(day_one_vis_ras) <- vis_levels 

levels(day_one_avg_ras) <- ifelse(params$DROP_LOW_AVG == "Yes", 
                                  avg_levels_wo_low,
                                  avg_levels_w_low)


# set extent of raster
extent(day_one_vis_ras) <- extent(c(grid_info[1], 
                                    grid_info[3],
                                    grid_info[2],
                                    grid_info[4]))

extent(day_one_avg_ras) <- extent(c(grid_info[1], 
                                    grid_info[3],
                                    grid_info[2],
                                    grid_info[4]))

# same crs as the doc.kml
crs(day_one_vis_ras) <- burn_crs$proj4string
crs(day_one_avg_ras) <- burn_crs$proj4string



## PREP POPULATION AND SVI DATA ----------------------------------------------

# create buffer around ignition to clip SVI/pop rasters
burn_buf <- st_buffer(burn_loc_sf, dist = 500000)

#SVI with buffer
svi_cr <- crop(svi, burn_buf, snap="out")                    
svi_fr <- rasterize(burn_buf, svi_cr) 
svi_buf <- mask(x=svi_cr, mask=svi_fr)

#pop with buffer
pop_cr <- crop(pop, burn_buf, snap="out")                    
pop_fr <- rasterize(burn_buf, pop_cr) 
pop_buf <- mask(x=pop_cr, mask=pop_fr)



## LEAFLET PLOTTING OF DAILY AVERAGE SMOKE AND VISUAL RANGE ----------------------------------------------

# vis color ramp
vis_col_ramp <- vis_pal %>% 
  pull(hex)
vis_col_ramp_hex <- vis_col_ramp[-c(14)]

# avg color ramp
avg_col_ramp <- avg_pal %>% 
  pull(hex)
avg_col_ramp_hex <- if(params$DROP_LOW_AVG == "Yes") avg_col_ramp[-c(1,9)] else avg_col_ramp[-c(9)]


# create color palette function for max
vis_pal_fun <- colorFactor(palette = vis_col_ramp_hex,
                       levels = levels(day_one_vis_ras)[[1]][1]$ID,
                       na.color = "transparent")

# create color palette function for avg
avg_pal_fun <- colorFactor(palette = avg_col_ramp_hex,
                       levels = levels(day_one_avg_ras)[[1]][1]$ID,
                       na.color = "transparent")

# create color palette function for SVI
svi_pal_fun <- colorBin(palette = "Purples",
  bins = c(seq(0, 1, 0.1)),
  na.color = "transparent")

# create color palette function for pop
pop_pal_fun <- colorFactor(palette = "magma",
                    levels = levels(pop_buf)[[1]][1]$ID,
                    reverse = TRUE,
                    na.color = "transparent")

# generate leaflet map for average smoke
avg_leaflet <- leaflet() %>% 
  addTiles() %>%
  
  # add mappanes to always keep smoke on top
  addMapPane("pop_map", zIndex = 410) %>% 
  addMapPane("svi_map", zIndex = 410) %>% 
  addMapPane("smoke_map", zIndex = 420) %>% 
  
  #daily average smoke conditions
  addRasterImage(day_one_avg_ras,
                colors = avg_pal_fun,
                opacity = 0.75,
                group = "Smoke",
           options=gridOptions(pane="smoke_map")) %>%
  addLegend(pal = avg_pal_fun,
           values = levels(day_one_avg_ras)[[1]][1]$ID,
           labFormat  = labelFormat(
             transform = function(x) {
             levels(day_one_avg_ras)[[1]]$pm[which(levels(day_one_avg_ras)[[1]]$ID == x)]}),
            opacity = 0.75,
           title = "PM2.5 (ug m^-3)",
           group = "Smoke") %>%

  # fire location
 addMarkers(data = burn_loc, lng = ~lon, lat = ~lat,
             icon = list(
               iconUrl = "redFlame.png",
               iconSize = c(25, 35))) %>% 

  # SVI data
  addRasterImage(svi_buf,
                 colors = svi_pal_fun,
                 opacity = 0.75,
                 group = "Social Vulnerability Index",
                 options= gridOptions(pane="svi_map")) %>%
  addLegend(pal = svi_pal_fun,
            opacity = 0.75,
            values = seq(0,1,0.1),
            group = "Social Vulnerability Index",
            position = "bottomleft",
            labels = seq(0,1,0.1),
            title = "Social Vulnerability Index") %>%

  # Pop data
  addRasterImage(pop_buf,
                 colors = pop_pal_fun,
                 opacity = 0.75,
                 group = "Population",
                 options= gridOptions(pane="pop_map")) %>%
  addLegend(pal = pop_pal_fun,
           values = levels(pop_buf)[[1]][1]$ID,
           labFormat  = labelFormat(
             transform = function(x) {
             levels(pop_buf)[[1]]$val[which(levels(pop_buf)[[1]]$ID == x)]}),
            opacity = 0.75,
           position = "bottomleft",
           title = "Population",
           group = "Population") %>% 

  # set scale of map viewer
  fitBounds(lng1 = burn_icon$x - 0.5,
            lat1 = burn_icon$y - 0.5,
            lng2 = burn_icon$x + 0.5,
            lat2 = burn_icon$y + 0.5) %>%

  # scale bar
  addScaleBar(position = "bottomright") %>% 
  
  # add layer control to map
  addLayersControl(
    overlayGroups = c("Smoke", "Population", "Social Vulnerability Index"),
    options = layersControlOptions(collapsed = FALSE)) %>% 
  hideGroup("Population") %>% 
  hideGroup("Social Vulnerability Index") 




# generate leaflet map for visual range
vis_leaflet <- leaflet() %>% 
  addTiles() %>%

  # plot visual range raster
  addRasterImage(day_one_vis_ras,
                 colors = vis_pal_fun,
                 opacity = 0.75) %>%
  addLegend(pal = vis_pal_fun, 
            values = levels(day_one_vis_ras)[[1]][1]$ID,
            labFormat  = labelFormat(
              transform = function(x) {
                levels(day_one_vis_ras)[[1]]$vis[which(levels(day_one_vis_ras)[[1]]$ID == x)]}),
            opacity = 0.75, 
            title = "Miles") %>% 
  
  ## fire location
  addMarkers(data = burn_loc, lng = ~lon, lat = ~lat,
             icon = list(
               iconUrl = "redFlame.png",
               iconSize = c(25, 35))) %>% 
  
  fitBounds(lng1 = burn_icon$x - 0.5,
            lat1 = burn_icon$y - 0.5,
            lng2 = burn_icon$x + 0.5,
            lat2 = burn_icon$y + 0.5) %>% 
  addScaleBar(position = "bottomright")


# remove smoke dispersion files from directory
unlink(outlook_path,
       recursive = TRUE)
```

__Average Daily Smoke Conditions on `r burn_info$date`:__ The average daily smoke conditions are helpful for concerns related to public health. Select 'Population' to see the number of people in each census tract surrounding the planned burn. Select 'Social Vulnerability Index' to see an index showing nearby vulnerable communities (0 = low vulnerability and 1 = high vulnerability).  
```{r avg_leaflet_map_show, out.width = "100%", include = TRUE, echo = FALSE, message = FALSE, warning = FALSE}

# show leaflet map
avg_leaflet

``` 

__Average Daily Visual Range Conditions on `r burn_info$date`:__ The average daily visual range conditions show estimated smoke impacts to visibility in the area. This map is useful for identifying potential impacts to visibility on roadways or other areas.
```{r vis_leaflet_map_show, out.width = "100%", include = TRUE, echo = FALSE, message = FALSE, warning = FALSE}

# show leaflet map
vis_leaflet

``` 

## Meteorological Conditions  

```{r firepoker_link, echo = FALSE, include = FALSE }

## Generate firepoker link

# read in dispersion breakpoints and id the state where burn is happening
disp_brkpts_df <- read_excel("disp_breakpoints.xlsx")
states <- st_read("states")
state_sf <- st_transform(states, crs = st_crs(burn_loc_sf))
burn_state <- as.character(states$STATE_ABBR[st_intersects(burn_loc_sf, state_sf)[[1]]])


disp_brkpts <- disp_brkpts_df %>% 
  filter(state == burn_state) 


  # create firepoker link
  fp_url <- paste("https://www.weather.gov/dlh/fwd?lat=",
                  round(burn_loc$lat, 3),
                  "&lon=",
                  round(burn_loc$lon, 3),
                  "&clat=38.967&clon=-97.267&zoom=7.000&basemap=stamenterrain&bbox=[-16540299.098,2518065.675,-5115162.882,6915872.719]&layers=USStates|ForecastDot|Domain|SurfaceFronts|Radar|&fwf=F&dispersion=",
                  paste(0, 
                        disp_brkpts[2], 
                        disp_brkpts[3],
                        disp_brkpts[4],
                        disp_brkpts[5],
                        sep = ","),
                  "&ndfd=WindGust",
                  sep = "")
```

The predicted weather data for this area, including fire behavior and smoke parameters can be found on the [Fire Weather Dashboard](`r fp_url`). `r if(!(is.null(params$SUPERFOG_SCREEN_SELECT))){superfog_sen}`



## Data Sources
AQI: EPA data accessed via https://github.com/MazamaScience/PWFSLSmoke

BlueSky Playground v3.5: https://portal.airfire.org/ 

Population: https://sedac.ciesin.columbia.edu/data/set/gpw-v4-population-count-rev11
  
Social Vulnerability Index: https://sedac.ciesin.columbia.edu/data/set/usgrid-us-social-vulnerability-index


 



